---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ForecastMoments

The joint forecast observation distribution for Gaussian variables can be described with 6 low-order moments.
'ForecastMoments' provides functions to compute these moments, and to interpret forecast quality using
a signal-plus-noise model based on these low-order moments. Uncertainty assessment of these moments and derived
forecast quality information including traditional verification scores and skill scores is provided based on 
parametric bootstrap resampling.

## Installation
The package can be installed from github.

```{r installation, eval=FALSE}
library(devtools)
install_github("jonasbhend/ForecastMoments")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ForecastMoments)

tm <- easyVerification::toymodel()
tmboot <- SNRresample(tm$fcst, tm$obs, c("EnsCorr", "Ens2AFC", "FairCrpss"))

summary(tmboot)
```

```{r example_plot, fig.width=8, fig.height=3}
boots <- summary(tmboot)
par(mfrow=c(1,nrow(boots) - 1)) 
tmp <- sapply(seq(1,nrow(boots)-1), function(i){
  hist(tmboot[i,-1], col='grey', main=rownames(tmboot)[i], xlab='')
  abline(v=boots[i,-3], lwd=2, lty=c(1,1,3,3), col=c(2,1,1,1))
  if (i == 1) legend("topleft", legend=colnames(boots)[-3], 
                     lwd=2, col=c(2,1,1,1), lty=c(1,1,3,3), 
                     cex=0.83, inset=0.05)
})
```
