---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ForecastMoments

The joint forecast observation distribution for Gaussian variables can be described with 6 low-order moments.
'ForecastMoments' provides functions to compute these moments, and to interpret forecast quality using
a signal-plus-noise model based on these low-order moments. Uncertainty assessment of these moments and derived
forecast quality information including traditional verification scores and skill scores is provided based on 
parametric bootstrap resampling.

## Installation
The package can be installed from github.

```{r installation, eval=FALSE}
library(devtools)
install_github("jonasbhend/ForecastMoments")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ForecastMoments)

tm <- easyVerification::toymodel()
summary(SNRresample(tm$fcst, tm$obs, c("EnsCorr", "FairCrpss")))
```
